Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

We will now present our quantitative methodology and the indicators we used in greater detail.

>>>>

As we attempt to measure the impact of education systems' support of students' self-confidence on the rate of entrepreneurship at the country-level, we expect to observe different effects depending if we consider entrepreneurial intentions only or we also look into actual entrepreneurial activities. Even in measuring the impact on activities, we could potentially observe different effects between nascent and established entrepreneurship. Therefore, we will consider the three measures of entrepreneursip separately:

1 Entrepreneurial Intentions

2 Nascent Entrepreneurship

3 Established Entrepreneurship

Having explained what lead us into this specific research design, we will now present our methodology for a quantitative analysis and the indicators that we used in greater detail.
